---
title: "Example hashtags and users"
author: "Morgan"
date: "12/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rtweet) # for harvesting tweets
library(tm) # for text mining
library(dplyr) 
library(tidyr)
library(data.table)
library(ggplot2)
library(ggthemes)
library(here)
library(tidyverse)
library(tidytext)
library(hms)#date and time
library(lubridate)#date and time
library(glue)# Data Wrangling and Visualization
library(cowplot)
library(magrittr)
library(plotly)
library(tidyverse)
library(tidytext)
library(widyr)# Data Wrangling and Visualization
library(tidytext)# Text Mining
library(tm)
library(wordcloud)# Text Mining
library(igraph)# Network Analysis
library(networkD3)# Network Visualization (D3.js)
library(ngram)# Network Visualization (D3.js)
library(syuzhet)# Sentiment analysis
library(ggraph)# misc libraries nathan uses
library(reshape2)
library(devtools)
library(SnowballC)# misc libraries nathan uses
```

Now that I've gotten myself acclimated, lets check into some of the assertions made by Visoughi (2008) regarding false news and the spread of misinformation
He claimed that "false news" spreaders
1. have fewer followers 
2. follow significantly fewer people
3. are less active 
4. are verified less often
5. are newer to Twitter

First I will search some hashtags that are reasonably related to false news (e.g., #climatecult #voterfraud. #voterfraud returned more tweets so I will proceed with that one)

```{r}
vf <- search_tweets("#voterfraud", n = 5000, include_rts = FALSE, retryonratelimit = FALSE)

#returned 8,262 tweets!
```

```{r}
vf <- vf %>% dplyr::select(user_id, created_at,screen_name,quoted_text, quoted_favorite_count, quoted_retweet_count, quoted_followers_count, quoted_friends_count, retweet_text, retweet_created_at, is_retweet, retweet_count, hashtags)

# hashtags are stored in a list tidyr has an answer for that
vf <- unnest(vf,cols=c(hashtags))

# probably too many to visualize so maybe just look at the top 20
top.20vf <- vf %>% filter(is.na(hashtags)==F) %>% 
             group_by(hashtags) %>% summarise(count=n()) %>% 
               arrange(-count) %>% filter(row_number() < 21) %>% 
                 arrange(count) %>% mutate(hashtags=factor(hashtags,levels=hashtags))
```

```{r}
ggplot(top.20vf,aes(x=hashtags,y=count)) + geom_bar(stat='identity') + 
  coord_flip() + theme_fivethirtyeight() + 
    ggtitle(label="Popular hashtags in tweets about #voterfraud",
            subtitle="hashtag use last 10 days") +
     theme(plot.title = element_text(size = 14, face = "bold"),
           plot.subtitle = element_text(face = "italic"))
```
#####################################################################
Attempting to filter by user_id and selet the top 30 info spreaders
```{r}
#examine which users are currently tweeting the most using this hashtag. I'm looking at the top 30 here...

vf_tweeters <- vf %>%
             group_by(user_id) %>% summarise(count=n()) %>% 
               arrange(-count) %>% filter(row_number() < 31) %>% 
                 arrange(count) %>% mutate(user_id=factor(user_id,levels=user_id))

#top vf tweeter ID and # of tweets:

#1282157417019711488	816
#67321785	322
#117910819	119
#831680442109665280	97
#315436946	94


#create vector of IDs from top "#voterfraud" tweeters, and lookup their account using the lookup_users function:
vf_users <- c(1282157417019711488, 67321785, 117910819, 831680442109665280,315436946)

fraud_tweeters <- lookup_users(vf_users)

## How many people do they each follow? # 

count(get_friends("Elizabe24953069")) #589
count(get_friends("CraigChamberlin")) #87
count(get_friends("RobinaRobbi")) #2328
count(get_friends("CarrieGeren")) #206
count(get_friends("sp1coli1983")) #501

#mean = 742.2

##How many followers do they each have?
count(get_followers("Elizabe24953069")) #141
count(get_followers("CraigChamberlin")) #5000 #max
count(get_followers("RobinaRobbi")) #425
count(get_followers("CarrieGeren"))  #85
count(get_followers("sp1coli1983")) #2499

#mean followers = 1630

#how active are these top "#voterfraud" tweeters?

## stream most recent 3200 tweets for each and graph by day
tmls_vftweeters <- get_timelines(c("CraigChamberlin", "Elizabe24953069", "RobinaRobbi", "CarrieGeren", "sp1coli1983"), n = 3200)

## plot the frequency of tweets for each user over time 
tmls_vftweeters %>%
  dplyr::filter(created_at > "2020-11-01") %>%
  dplyr::group_by(screen_name) %>%
  ts_plot("days", trim = 1L) +
  ggplot2::geom_point() +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "bottom",
    plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of Twitter statuses posted by top #voterfraud tweeters",
    subtitle = "Twitter status (tweet) counts aggregated by day from November 01 2020",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )

#Most CraigChamberlin with >300, sp1coli983 has ~200 per day, Elizbe ~130 at times...
```

```{r}
#verified?
## select one or more twitter users to lookup
users <- c(
  "CraigChamberlin", "Elizabe24953069", "RobinaRobbi", "CarrieGeren", "sp1coli1983"
)

#is verified?
vf_verified_tweets <- tmls_vftweeters %>%
subset(verified) #object is empty. I will also look up each user on Twitter

#I chose to look up each person by hand to see when they created their account

#CraigChamberlin # August 2009 #not verified
#Elizabe24953069 # July 2020  #not verified
#RobinaRobbi  #February 2010  #not verified
#CarrieGeren  #February 2020  #not verified
#sp1coli1983   #June 2010  #not verified

```


```{r}
t <- search_tweets("#wearamask", n = 5000, include_rts = FALSE, retryonratelimit = TRUE)

wmt <-t

```


```{r}
wmt <- wmt %>% dplyr::select(user_id, created_at,screen_name,quoted_text, quoted_favorite_count, quoted_retweet_count, quoted_followers_count, quoted_friends_count, retweet_text, retweet_created_at, is_retweet, retweet_count, hashtags)

# hashtags are stored in a list tidyr has an answer for that
wmt <- unnest(wmt,cols=c(hashtags))
# probably too many to visualize so maybe just look at the top 20
top.20wmt <- wmt %>% filter(is.na(hashtags)==F) %>% 
             group_by(hashtags) %>% summarise(count=n()) %>% 
               arrange(-count) %>% filter(row_number() < 21) %>%
                 arrange(count) %>% mutate(hashtags=factor(hashtags,levels=hashtags))
```

```{r}

ggplot(top.20wmt,aes(x=hashtags,y=count)) + geom_bar(stat='identity') + 
  coord_flip() + theme_fivethirtyeight() + 
    ggtitle(label="Popular hashtags in tweets about #wearamask",
            subtitle="hashtag use last 10 days") +
     theme(plot.title = element_text(size = 14, face = "bold"),
           plot.subtitle = element_text(face = "italic"))
```

```{r}

wmusers <- wmt %>%
             group_by(user_id) %>% summarise(count=n()) %>% 
               arrange(-count) %>% filter(row_number() < 31) %>%
                 arrange(count) %>% mutate(user_id=factor(user_id,levels=user_id))

#top 5 users:
#1263925248317173760	#916
#388368711	#646
#864999784049803264	#608
#73747558	#511
#252563614	#490


users2 <- c(1263925248317173760, 388368711,864999784049803264, 
          73747558,252563614)
           
wm_tweeters <- lookup_users(c(users2))


## How many people do they each follow? # 
count(get_friends("Starbright_2")) #898
count(get_friends("ChimpReports")) #1069
count(get_friends("Bompi_Tortilli")) #1762
count(get_friends("GreggMasters")) #1496
count(get_friends("CapeTownTrains")) #932

##How many followers do they each have?
count(get_followers("Starbright_2")) #23
count(get_followers("ChimpReports")) #5000
count(get_followers("Bompi_Tortilli")) #219
count(get_followers("GreggMasters")) #3196
count(get_followers("CapeTownTrains")) #5000

#how active are these users?

## stream most recent 3200 tweets for each and graph by day

tmls_wmtweeters <- get_timelines(c("Starbright_2", "ChimpReports", "Bompi_Tortilli", "GreggMasters", "CapeTownTrains"), n = 3200)

## plot the frequency of tweets for each user over time
tmls_wmtweeters %>%
  dplyr::filter(created_at > "2020-11-01") %>%
  dplyr::group_by(screen_name) %>%
  ts_plot("days", trim = 1L) +
  ggplot2::geom_point() +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "bottom",
    plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of Twitter statuses posted by news tweeters",
    subtitle = "Twitter status (tweet) counts aggregated by day from November 2020",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )

#is verified?
wm_verified_tweets <- tmls_wmtweeters %>%
subset(verified) #these are verified

#I chose to look up each person by hand to see when they created their account
 #Starbright_2 # May 2020
 #ChimpReports # October 2010 VERIFIED
 #Bompi_Tortilli #May 2017 
 #GreggMasters #September 2009 
 #CapeTownTrains #February 2011
```
So -- what about my original research question?

Visoughi (2008) re false news and the spread of misinformation claimed that "false news" spreaders had:

- fewer followers 
- follow significantly fewer people 
- were less active 
- verified less often 
- newer to Twitter )

**RESULTS In our sample 
mean followers 
- voter fraud: 1,630 , wear mask: 2,688
mean friends 
- voter fraud: 742, wear mask: 1231.4
avtivity (graph):
- voter fraud summary (three frequent tweeters):
  -CraigChamberlin with >300 
  -p1coli983 has ~200 per day
  -Elizbe ~130 at times...
- wear mask summary (one frequent tweeter):
  -CapeTownTrains highest daily # <150
  
twitter tenure & verification:
- voter fraud: avg 6.5
 CraigChamberlin 11 years (August 2009) #not verified
 Elizabe24953069 < 1 year  (July 2020)  #not verified
 RobinaRobbi  10 years (February 2010)  #not verified
 CarrieGeren  <1 year (February 2020)  #not verified
 #sp1coli1983 10 years (June 2010)  #not verified
 
- wear mask: avg 6.7
Starbright_2 <1 year (May 2020) #not verified
ChimpReports  10 years (October 2010) VERIFIED
Bompi_Tortilli >3 years (May 2017) #not verified
GreggMasters 11 years (September 2009 ) #not verified
CapeTownTrains 9 years (February 2011) #not verified

- fewer followers (supported by our sample)
- follow significantly fewer people (supported by our sample)
- were less active (NOT supported by our sample)
- verified less often (supported by our sample)
- newer to Twitter (marginally supported by our sample, but not by much - distrubutions looks bimodal)

 ##### EXTRA: FUN WITH NETWORKS ##### (code from Michael Kearney)
See this helpful link: https://mkearney.github.io/nicar_tworkshop/#36

Let's scope out the friend networks for the POIs from each group above...

```{r}
## get friends of multiple accounts - vf top tweeters
vf_fds <- get_friends(c("CraigChamberlin", "Elizabe24953069", "RobinaRobbi", "CarrieGeren", "sp1coli1983"))
## frequency count of accounts followed by the users queried above
tbl <- table(vf_fds$user_id)
## subset fds data to only those followed by 3 or more
vf_fds3 <- subset(vf_fds, user_id %in% names(tbl[tbl > 2L]))
## convert fds3 to matrix
mat <- as.matrix(vf_fds3)
## convert to graph object
mat <- igraph::graph_from_edgelist(mat)
## plot network
vf_network <- plot(mat)
```

```{r}
## get friends of multiple accounts - wearmask top tweeters
wm_fds <- get_friends(c("Starbright_2", "ChimpReports", "Bompi_Tortilli", "GreggMasters", "CapeTownTrains"))
## frequency count of accounts followed by the users queried above
tbl2 <- table(wm_fds$user_id)
## subset fds data to only those followed by 3 or more
wm_fds3 <- subset(wm_fds, user_id %in% names(tbl2[tbl2 > 2L]))
## convert fds3 to matrix
mat2 <- as.matrix(wm_fds3)
## convert to graph object
mat2 <- igraph::graph_from_edgelist(mat2)
## plot network
wm_network <- plot(mat2)
```



